25-Figure3-051821

### 2021-11-18 notebooks/02-Figure2-051321.Rmd
fixed getting input name from snakemake in notebooks

```{r}
if(snakemake@params['save']==TRUE){
  figure_folder = "../reports/figures/paper_figures_052521/"
combined_plot <- plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.2, .3))
ggsave(glue("{figure_folder}/fig2.png"),plot=combined_plot,width=12,height=12)
}
```

>>>>

```{r}
if(snakemake@params['save']==TRUE){
  figure_folder = "reports/figures/paper_figures_052521/"
combined_plot <- plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.2, .3))
ggsave(glue("{figure_folder}/fig2.png"),plot=combined_plot,width=12,height=12)
}
```

### 2021-11-18 notebooks/03-Fig3abde_4acd-051821.Rmd
fixed getting input name from snakemake in notebooks

```{r}
#if(snakemake@params['save']==TRUE){
  figure_folder = "../reports/figures/paper_figures_052521/"
ggsave(glue("{figure_folder}/fig3a.png"),plot=sensor_neighbor_degree_plot,width=3,height=3)
ggsave(glue("{figure_folder}/fig3b.png"),plot=sensor_connectivity_plot,width=3.5,height=2.5)
ggsave(glue("{figure_folder}/fig3d.png"),plot=sens_deg_comp+theme(legend.position='none'),width=3.9,height=2.1)
ggsave(glue("{figure_folder}/fig3e.png"),plot=sens_sens_comp+theme(legend.position='none'),width=3.9,height=2.1)

>>>>

```{r}
#if(snakemake@params['save']==TRUE){
  figure_folder = "reports/figures/paper_figures_052521/"
ggsave(glue("{figure_folder}/fig3a.png"),plot=sensor_neighbor_degree_plot,width=3,height=3)
ggsave(glue("{figure_folder}/fig3b.png"),plot=sensor_connectivity_plot,width=3.5,height=2.5)
ggsave(glue("{figure_folder}/fig3d.png"),plot=sens_deg_comp+theme(legend.position='none'),width=3.9,height=2.1)
ggsave(glue("{figure_folder}/fig3e.png"),plot=sens_sens_comp+theme(legend.position='none'),width=3.9,height=2.1)
